---
title: "Package 'stringCompare'"
author: "Prathwish Shetty"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Package 'stringCompare'}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



## String comparison techniques implemented in the package

1. *Extended Jaccaard*
2. *Monge Elkan*


### 1. Extended Jaccard comparison

####Description

This algorithm extracts tokens (words sererated by whitespace) from the two input strings and then find the best matching pair of tokens in the set of tokens using a secondary similarity function.

####Usage

extendedJaccard(*string1*,*string2*,*method=c("osa","lv","dl","lcs","jw")*,*threshold=seq(1,0)*)

####Arguements

* **string1** - *character string to be matched*
* **string2** - *character string to be matched against*
* **method**  - *Method to be used for secondary comparison*
* **threshold**- *Numeric vector of probabilities with values in [0,1]*

####Details

This is an extension of the Jaccard algorithm, best suited for strings with multiple words. It uses a secondary string comparison method to calculate similarity between all the words in the two strings to be compared.Next a set of tokens shared between the two strings are calculated provided the similarity is above a certain threshold. Finally, to get the similarity score a ratio of shared tokens by sum of shared tokens and unique 
tokens of the two strings.

####Value

Returns a vector with similarities, which are values between 0 and 1 where 1 corresponds to perfect similarity (distance 0) and 0 to complete dissimilarity.

####Methods that can be used as secondary similarity function

* **lv** - *Levenshtein similarity*
* **osa** - *Optimal string aligment similarity*
* **dl**  - *Full Damerau-Levenshtein similarity*
* **lcs**  - *Longest common substring similarity*
* **jw**  - *Jaro Winkler similarity*

####Example

```{r}
#calculate the similarity between two strings "kaspersky antivirus" and "kasper antivirus"
stringCompare::extendedJaccard("Caspersky is awesome","Casper are antivirus","jw",0.85)
```



### 2. Monge - Elkan String comparison

####Description

This algorithm extracts tokens (words sererated by whitespace) from the two input strings and then find the best matching pair of tokens in the set of tokens using a secondary similarity function.

####Usage

mongeElkan(*string1*,*string2*,*method=c("osa","lv","dl","lcs","jw")*)

####Arguements

* **string1** - *character string to be matched*
* **string2** - *character string to be matched against*
* **method**  - *Method to be used for secondary comparison*

####Details

This method separates a string into tokens based on white spaces. And then each token from one string is compared  against  every  other  token  in  another  string  using  a  secondary  comparison  method.  Next  the average of the best match per token is taken to compute the Monge-Elkan Similarity score.

####Value

Returns a vector with similarities, which are values between 0 and 1 where 1 corresponds to perfect similarity (distance 0) and 0 to complete dissimilarity.

####Methods that can be used as secondary similarity function

* **lv** - *Levenshtein similarity*
* **osa** - *Optimal string aligment similarity*
* **dl**  - *Full Damerau-Levenshtein similarity*
* **lcs**  - *Longest common substring similarity*
* **jw**  - *Jaro Winkler similarity*

####Example


```{r}
#calculate the similarity between two strings "kaspersky antivirus" and "kasper antivirus"

stringCompare::mongeElkan("Caspersky antivirus","Casper antivirus","jw")
```

